Meta-analysis

### 2019-10-23 05_MetaAnalysis.Rmd
Remove Trycatch error handling

source("R/AUS_rainfall_function.r")

# loop to download and save all the rainfall sum data

@@

      #ERROR HANDLING
     # possibleError <- tryCatch(
         rain_dat_sum$rainfall_sum[i] <- 
            AUS_rainfall(StartDate = as.Date(rain_dat_sum$planting_date)[i] + 10,
                         EndDate = as.Date(rain_dat_sum$planting_date)[i] + 90,
                         lat = rain_dat_sum$lat[i],
                         long = rain_dat_sum$lon[i])
         #error=function(e) e
         #)

      #if(inherits(possibleError, "error")) {print(possibleError)
      #   next
      }
   }

@@

write.csv(lm_data, "data/rainfall_x_Gyield_lmod.csv")
<- read.csv("data/rainfall_x_Gyield_lmod.csv", stringsAsFactors = FALSE)
rain_dat_sum[rain_dat_sum$location != "Hermitage",] %>%
   ggplot(aes(x = rainfall_sum, y = grain_yield )) + 
   geom_point(aes(colour = location)) +
   geom_smooth(method = "lm")

>>>>

source("R/AUS_rainfall_function.r")
# loop to download and save all the rainfall sum data

@@

         rain_dat_sum$rainfall_sum[i] <- 
            AUS_rainfall(StartDate = as.Date(rain_dat_sum$planting_date)[i] + 10,
                         EndDate = as.Date(rain_dat_sum$planting_date)[i] + 90,
                         lat = rain_dat_sum$lat[i],
                         long = rain_dat_sum$lon[i])

      }
   }

@@

#write.csv(lm_data, "data/rainfall_x_Gyield_lmod.csv")
lm_data <- read.csv("data/rainfall_x_Gyield_lmod.csv", stringsAsFactors = FALSE)
rain_dat_sum[rain_dat_sum$location != "Hermitage",] %>%
   ggplot(aes(x = rainfall_sum, y = grain_yield )) + 
   geom_point(aes(colour = location)) +
   geom_smooth(method = "lm")
